---
title: "Target Markdown"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

Target Markdown is a powerful R Markdown interface for reproducible analysis pipelines, and the chapter at https://books.ropensci.org/targets/markdown.html walks through it in detail. This R Markdown report the example from the chapter. Try it out in both interactive and non-interactive modes, either by running the code chunks in different ways or setting the `tar_interactive` chunk option.

# Packages

The example requires several R packages, and `targets` must be version 0.5.0.9000 or above. 

```{r, eval = FALSE}
install.packages(c("biglm", "dplyr", "ggplot2", "readr", "targets", "tidyr"))
```

# Setup

If you are using old versions of `targets` (<= 0.7.0) and/or `knitr` (<= 1.33), you will need to load the `targets` package in the R Markdown document in order for Target Markdown code chunks to work.

```{r}
library(targets)
```

Near the top of the document, you may also wish to remove the `_targets_r` directory previously written by non-interactive runs of the report. Otherwise, your pipeline may contain superfluous targets.

```{r}
library(targets)
tar_unscript()
```

# Globals

We first define some global options/functions common to all targets. The function below plots a histogram of ozone concentrations, and our histogram target will need it.

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)

tar_option_set(packages = c("RJobTissueArea","tibble", "readr", "dplyr", "ggplot2"))

source("R/helpers_DBrelated.R")

```

# Targets

Our first target borrows the `airquality` dataset built into base R.

```{targets setGroupID}
tar_target(group_ID, "P1761451")
```
```{targets queryGroupID}
tar_target(query_result,
           query_mongoDB("limslager","UID",group_ID))
```
```{targets extractEDL}
tar_target(EDL,
           query_result%>%
             get_EDL_from_query_result()
)
```

```{targets extractChipIDs}
tar_target(chip_IDs,
           extract_chipIDs_from_groupEDL(EDL)
)
```

```{targets findValidChipIDs}
tar_target(validChipIDs,
               chip_IDs%>%
             check_if_chip_data_exist())
```

```{targets findValidGroupChipIDs}
tar_target(valid_chipIDs,
           find_valid_group_chip_IDs(group_ID))
```


# Pipeline

If you ran all the `{targets}` chunks in non-interactive mode, then your R scripts are set up to run the pipeline.

```{r}
tar_make()
```

# Output

You can retrieve results from the `_targets/` data store using `tar_read()` or `tar_load()`.


```{r}
tar_load(group_ID)
#tar_read(query_result)
tar_read(validChipIDs)
tar_read(valid_chipIDs)
```


```{r}
tar_visnetwork()
```

At this point, you can go back and run `{targets}` chunks in interactive mode without interfering with the code or data of the non-interactive pipeline.
