---
title: " documentation - find_all_ImageFiles"
subtitle: "reportings on functional development"
author: "Julia Ortmann"
output: 
  html_document:
    code_folding: show
    number_sections: yes
    toc: yes
    toc_depth: '3'
    theme:
      bg: "#202123"
      fg: "#B8BCC2"
      primary: "#EA80FC"
      secondary: "#00DAC6"
      base_font:
        google: Prompt
      heading_font:
        google: Proza Libre
abstract: The aim of this build functions for import of scan HDR images, defined by scan_ID
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_file = "inst/report/dev report - find all image files.html",
      envir = globalenv()
    )
  })
---

```{r setup, include=FALSE}
if (requireNamespace("thematic")) 
  thematic::thematic_rmd(font = "auto")
```

# summary

## import chip group

- find_valid_group_chip_IDs() in helpers: RJob_execution

```{r}
group_ID <- "P1761451"
chip_IDs <- find_valid_group_chip_IDs(group_ID)
```

## find all image files

- create_working_directory() in helpers: RJob_execution

```{r}
output_dir <- "devel/data/data_output"
RJobTissueArea:::create_working_directory(output_dir)
```

- export_list_all_image_files() in helpers: ImportBlobFiles

```{r}
image_files <- export_list_all_image_files(chip_IDs,
                                           group_ID,
                                           output_dir)
```

- create_result_filepath() in helpers: ImageProcessing

```{r}
file <- create_result_filepath(output_dir,
                               name_string = "all_image_files_of_groupID",
                               result_ID=group_ID,
                               type = "csv")
image_files <- data.table::fread(file)
```

- select_valid_image_files() in helpers: ImportBlobFiles

```{r}
blob32_files <- select_valid_image_files(image_files,
                                         type = "blob32")
```

# introduction 

- map over chip_IDs
- find scan_IDs 
- find positions measured and subselected (TO DISCUSS)
- select approbriate scan images
- import blob files
- set grey value threshold
- sum tissue-pixels and position-pixel
- calculate tissue AREA and POSITION AREA
- count cells
- export chipID cell_count tissue and position area 

# find all Blob ImageFiles {.tabset .tabset-pills}

- define group_ID
- find all valid chip_IDs in group
- create MethodHistory for each valid chip in group
- extract ScanHistories from MethodHistories
(- wrangle to IDs and remove Excluded Scans)
- add chip_path and imageServer_path
- add ScanHistory
(- filter excluded scans)
- add ScanBasePath, PositionFolders
- query scanIDs in scans-collection
- get image Type of each Scan
- add HDRimage_filepath, FLimage_filepath, posRefimage_filepath depending on imageType
- add BlobFileName
- declare imageType (by available filepath of the available BlobFile of a given scanID)
- wrangle to df containing IDs and corresponding BlobFileNames of each scan
- check for missing  scans

**querry scan_ID in collection scans results in**

```{r,eval=FALSE}
result <-query_mongoDB("scans",
              "channelUID",
              chip_IDs)
```

- a dataframe without EDL field filled
- important containing columns:

    + basepath= chip_path
    + jobType either TL or FL 
    + UID = scan_ID
    + channelUID = chip_ID

- good to know columns: 

    + imageRotation
    + positionCount
    + hardware, df containing columns: "camera-serial", "camera-model", "camera-vendor", "camera-exposure"   "camera-binning", "camera-gain", "microscope-serial" "microscope-model"  "microscope-vendor" "objective-unq", "objective-name", "reflector-unq", "reflector-name", "optovar-unq",  "optovar-name", "sideport-unq", "sideport-name", "lightsources"
    + positions, df containing columns: "posid", "focusOffset", "enabled", "focusInterpolated" "chipx", "chipy", "stageX", "stageY", "stageZ", "imagePixDX", "imagePixDY", "imageRotation", "posref", "hdr", "focus","filimages",deltaTL", "bleach-time"  
    
    + columns "posref" and "focus" are df's, containing the columns: "img-ref", "datahash", "hashtype", "filename", "filepath", "pbytes"
    column "deltaTL"is a list of df's, each containg the columns: "img-ref", "datahash", "hashtype", "filename", "filepath", "pbytes", "deltaZ"
    
## functions {.tabset .tabset-pills}

### create_pos_foldername

```{r}
create_pos_foldername <- function(imageServer_path,basePath,pos_ID){
  
  file.path(imageServer_path,basePath,
                    paste0("pos",pos_ID))
}
```

### query_filterset_of_scanIDs()

```{r}

query_filterset_of_scanIDs <- function(scan_IDs){
  
  # query scanIDs in scans
  query_scan_scans <- query_UID_limsproc(scan_IDs)

  # get EDL
  EDL <-get_EDL_from_query_result(query_scan_scans)
  
  # select node: Active Filterset-ID
  filterset <- purrr::map_chr(EDL,
                              ~.x%>%xml2::read_xml()%>%
                                xml2::xml_find_all('/Method/Machine/SpecificParameters/SpecificParameter[@Name = "Active Filterset-ID"]')%>%
                                xml2::xml_attr("Value"))
  
  return(filterset)
  
}
```

### create_ScanHistory_of_chipIDs()

```{r}
create_ScanHistory_of_chipIDs<-function(chip_IDs){

  MethodHistory <- create_MethodHistory_of_chipIDs(chip_IDs)

  ScanHistorys <- purrr::map(MethodHistory,
                             ~.x%>%
                               dplyr::rename("scan_ID" = "UID")%>%
                               dplyr::rename("cycle_ID" = "CycleUID")%>%
                               tidyr::fill(cycle_ID,  .direction = "up")%>%
                               dplyr::filter(Type == "Chipcytometry-Scan")%>%
                               dplyr::select(scan_ID,cycle_ID,Status,Tag,Excluded,PreparedForDataviz))
  return(ScanHistorys)
}
```

### query_UID_limsproc()

```{r}

query_UID_limsproc<- function(chip_IDs){

  V <- 130222 # initial Version
  V <- 080322
  #- added return(result)
  #____________________________

  result <- query_mongoDB("limsproc",
                          "UID",
                          chip_IDs)

  return(result)
}
```

## workflow

```{r}

tictoc::tic("find image files complete workflow")

# load library
library(RJobTissueArea)

# define group ID
group_ID <- "P1761451"

# find valid group chip_IDs
chip_IDs <- find_valid_group_chip_IDs(group_ID)
chip_IDs <- chip_IDs

# find server paths
server_paths <- find_server_path()
server_paths <- server_paths$server_path

# find chip_path
chip_paths <- purrr::map_chr(chip_IDs,
                         ~find_chip_path(.x,server_paths))

# wrangle to imageServer_path
imageServer_paths <- purrr::map2_chr(chip_paths,chip_IDs,
                    ~stringr::str_remove(.x,.y))

IDs <- dplyr::tibble(
  chip_ID = chip_IDs,
  chip_path = chip_paths,
  imageServer_path = imageServer_paths)

# create scanHistory
ScanHistory = create_ScanHistory_of_chipIDs(chip_IDs)%>%
  dplyr::bind_rows()

# add filterset
ScanHistory <- ScanHistory%>%
  dplyr::mutate(filterset = query_filterset_of_scanIDs(scan_ID))

# query result chipID ins scans
query_chip_scans <- query_mongoDB("scans",
                                  "channelUID",
                                  chip_IDs)

# select columns
results_chip_scans <- purrr::map(query_chip_scans$result,
                  ~.x%>%
                    dplyr::select("chip_ID" = "channelUID",
                                  "scan_ID" = "UID",
                                  jobType,
                                  basePath,
                                  "Status" = "jobEndState",
                                  positions,
                                  `enabled-count`))

# subselect columns position
results_chip_scans <- purrr::map(
  results_chip_scans,
  ~.x%>%
    tidyr::unnest(cols="positions")%>%
    dplyr::select(
      dplyr::any_of(c("chip_ID", 
                  "scan_ID", 
                  "pos_ID" = "posid", 
                  "jobType", 
                  "basePath", 
                  "Status", 
                  "chipx", 
                  "chipy", 
                  "enabled",
                  "bleach-time",
                  "enabled-count"))))

results_chip_scans <- results_chip_scans%>%
  dplyr::bind_rows()

results_chip_scans%>%head()

# join imageServer_path
result_paths <- dplyr::left_join(results_chip_scans,
                           IDs,
                           by = "chip_ID")

# add pos_path
result_paths <- result_paths%>%
  dplyr::mutate(pos_path = create_pos_foldername(imageServer_path,
                                                   basePath,
                                                   pos_ID))

# add dirs in pos_path
result_paths <- result_paths%>%
  dplyr::mutate(image_folder = purrr::map(pos_path,
                                          ~list.dirs(.x,
                                                     full.names = FALSE,
                                                     recursive = FALSE)))%>%
  tidyr::unnest(cols="image_folder")%>%
  dplyr::mutate(image_path = file.path(pos_path,image_folder))

# list files in image_folder
result_files <- result_paths%>%
  dplyr::mutate(blob_filename = purrr::map(image_path,
                                          ~list.files(.x)))%>%
  tidyr::unnest(cols="blob_filename")

# add filetype
result_files <- result_files%>%
  dplyr::mutate(filetype = tools::file_ext(blob_filename))

head(result_files)

# join ScanHistory
result_files <- dplyr::left_join(
  result_files,
  ScanHistory,
  by = c("scan_ID", "Status"))

head(result_files)

# remove excluded scans
result_files <- result_files%>%
  dplyr::filter(Excluded %in% c(NA, "FALSE"))%>%
  dplyr::filter(Status == "Finished")

# filter blob files
blob_result_files <- result_files%>%
  dplyr::filter(filetype %in% c("blob","blob32"))

# filter png files
png_result_files <- result_files%>%
  dplyr::filter(filetype %in% c("png"))

tictoc::toc()
```
