---
title: " documentation - image processing"
subtitle: "reportings on functional development"
author: "Julia Ortmann"
output: 
  html_document:
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: '3'
    theme:
      bg: "#202123"
      fg: "#B8BCC2"
      primary: "#EA80FC"
      secondary: "#00DAC6"
      base_font:
        google: Prompt
      heading_font:
        google: Proza Libre
abstract: The aim of this build functions for import of scan HDR images, defined by scan_ID
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_file = "inst/report/dev report - process hdr images - data_sum approach.html",
      envir = globalenv()
    )
  })
---

```{r setup, include=FALSE}
if (requireNamespace("thematic")) 
  thematic::thematic_rmd(font = "auto")
```

# summary

# introduction 

**process modules**

A) import chip group
B) find all image files
  - find all files
  - read all blob.xml
  - import blob image
C) image processing steps:

  1) sum pixel of all hdr imgages
  2) convert pixel matrix to pixmapGrey object
  3) blurring via gauss filter
  4) binary filtering via threshold
  5) export tiff-images

D) estimation of tissue size

  1) tissue size estimation (via pixel resolution and amount pixels set TRUE)
  2) return tissue area results (tissue size [mm] and %tissue size)

--> apply on parameterset, positions, chips


# workflows

## import chip group

- find_valid_group_chip_IDs() in helpers: RJob_execution

```{r}
library(RJobTissueArea)
group_ID <- "P1761451"
chip_IDs <- find_valid_group_chip_IDs(group_ID)
```

## find all image files

- create_working_directory() in helpers: RJob_execution

```{r}
output_dir <- "devel/data/data_output"
RJobTissueArea:::create_working_directory(output_dir)
```

- create extended Version of ScanHistory

```{r, eval=FALSE}
ScanHistory <- create_ScanHistory_extended(chip_IDs,
                                           output_dir, 
                                           result_ID = group_ID)
```

- read ScanHistory

```{r}
filename <- create_result_filepath(output_dir,
                                   "extendedScanHistory",
                                   group_ID,
                                   "csv")

ScanHistory <- data.table::fread(filename)
ScanHistory%>%head()
```

- select valid entities

```{r}
result_files <- select_valid_image_files(ScanHistory,type = NULL)
result_files%>%head()
```

- select hdr images and add filepath

```{r}
hdr_files <- select_hdr_files(result_files)
hdr_files%>%head()
```

## generate data_sum

- create list of image_groups:
    + nest file groups (by chip_ID and pos_ID) to a image_selection_list
    + add group_ID 
    + add filename of the file containing the data_sum results to be created

```{r}
image_groups <- hdr_files%>%
  dplyr::rename("image_path" = "hdr_filepath",
                "blob_filename" = "hdr_filename")%>%
  dplyr::group_by(chip_ID,pos_ID)%>%
  tidyr::nest()%>%
  dplyr::mutate(group_ID = paste0(chip_ID,"_",pos_ID))%>%
  dplyr::mutate(data_file = create_result_filepath(output_dir,
                                                   "data_sum",
                                                   group_ID,
                                                   type="csv"))
image_groups%>%head
image_groups$data[1][[1]]%>%head
```
- set output_dir for data_sum results

```{r}
output_dir_dataSum <- file.path(output_dir,"data_sum_collection_2")
```

- create_export_data_sum () in helpers: ImageProcessing Version:030522

    + import all images of a image group
    + calculate data_sum of all pixel values 
    + return one image matrix
    + exports data_sum into the output_dir
    + apply to each chip group

```{r, eval=FALSE}
image_groups_resolution <- purrr::map2(image_groups$data,
                                       image_groups$group_ID,
                                       ~create_export_data_sum(.x,
                                                               .y,
                                                               output_dir_dataSum))
```

data_sum_resultion: 
[1] 0.3697953 0.6639183
attr(,"resolution_unit")
[1] "[um per pixel edge]"

- read in single file: data_sum

```{r}
group_ID <- image_groups$group_ID[1]
image_group_list <- image_groups$group_ID
result_filename <- create_result_filepath(output_dir_dataSum,
                                            "data_sum",
                                            group_ID,
                                            type="csv")
data_sum <- data.table::fread(result_filename)
```

## image processing



### variables

- **variables**

```{r}
#variables
chip_ID <- "M"
pos <- 1
cellres <- c(1,1)
sigma <- 0.5
threshold <- 4
output_dir <- "inst/data/data_output"
cols <- 1040
rows <- 1392
```

- **secundary variable**

```{r}
#secundary vaiables
result_ID <- create_name_result_ID(chip_ID,
                                   pos,
                                   sigma,
                                   threshold
                                   )
```

### function definition

#### **perform_image_processing() - workflow function**

```{r}
create_pixmapGrey(data_sum,
                  cellres,
                  output_dir,
                  chip_ID,
                  pos,
                  sigma,
                  threshold)

perform_image_processing <- function(data_sum,
                              cellres = cellres,
                              output_dir = output_dir,
                              chip_ID,
                              pos,
                              sigma = sigma,
                              threshold = threshold){
  
  # create data.sum
  
  # export data.sum
  
  # read data_sum
  
  # define data_sum as matrix
  m.data_sum <- data.sum%>%
    as.matrix()

  # create pixmap
  # cellres: pixel resolution in horizontal and vertical direction
  image <-pixmap::pixmapGrey(m.data_sum,
                             nrow = rows,
                             ncol = cols,
                             cellres=cellres)
  
  # get grey values
  grey_values <- image@grey * 255
  
  # Low-pass Gaussian filter
  xb <- EBImage::gblur(grey_values,
                       sigma)
  # round values
  xb <- round(xb,digits = 1)
  
  # create blurred pixmap image
  image_blurred <- pixmapGrey(xb,
                              cellres=cellres) 
  
  #threshold filtering
  pos <- which(xb > threshold)
  xt <- xb
  xt[which(xb > threshold)] <- 1
  xt[which(xb <= threshold)] <- 0
  
  # pixmap object of binary image
  image_binary <- image
  image_binary@grey <- xt

  # create tiff of result images
  export_image_result_tiffs(image,
                            image_blurred,
                            image_binary,
                            output_dir,
                            chip_ID,
                            pos,
                            sigma,
                            threshold,
                            cols,
                            rows)
  
}
```

#### **export_image_result_tiffs()**

```{r}
export_image_result_tiffs <- function(image,
                                      image_blurred,
                                      image_binary,
                                      output_dir,
                                      chip_ID,
                                      pos,
                                      sigma,
                                      threshold,
                                      cols,
                                      rows){
  # filename
  result_ID <- create_name_result_ID(chip_ID,
                                     pos,
                                     sigma,
                                     threshold)
  # complete filepath
  file <- create_result_filepath(
    output_dir,
    "result_tiffs",
    result_ID,
    "tiff"
  )
  
  # create tiff object
  tiff(filename = file,
       width = cols*3,
       height = rows)
  
  par(mfrow=c(1,3))
  
  # plot inital image
  plot(image,
       main = "grey value image",
       sub = "sum values by pixels across all hdr images")

  # plot blurred image
  plot(image_blurred,
       main = paste0("blurred with sigma = ",sigma),
       sub = paste0("min: ", min(xb), "max: ",max(xb)))
  
  # plot binary image
  plot(image_binary,
       main= paste0("threshold set to: ",threshold))
  
  dev.off()
  
  writeLines(c(
    paste0("- successful exported processed image results")
    ))
}
```

#### **create_name_result_ID()**

```{r}
create_name_result_ID <- function(chip_ID,
                                  pos,
                                  sigma,
                                  threshold){
  
  result_ID <- paste0("chipID_",chip_ID,
                      "_pos_",pos,
                      "_sigma_",sigma,
                      "_threshold_",threshold)
}
```

#### **create_result_filepath()**

```{r}
create_result_filepath <- function(output_dir,
                                   name_string,
                                   result_ID,
                                   type){
  
  path <- file.path(
    output_dir,
    paste0(name_string,
           "_",result_ID,
           ".",type))
  
  return(path)
}
```

### workflow application

```{r}

```










# supplement

## workflow - import image data

- define chip_group and output_dir

```{r, eval=FALSE}
library(RJobTissueArea)
output_dir <- "devel/data/data_output"
group_ID <- "P1761451"
```

- create_working_directory() in helpers: RJob_execution

```{r, eval=FALSE}
RJobTissueArea:::create_working_directory(output_dir)
```

- load all chip_IDs in the group

```{r, eval=FALSE}
chip_IDs <- find_valid_group_chip_IDs(group_ID)
```

- create extended Version of ScanHistory

```{r, eval=FALSE}
ScanHistory <- create_ScanHistory_extended(chip_IDs,
                                           output_dir, 
                                           result_ID = group_ID)
```

- read ScanHistory

```{r, eval=FALSE}
filename <- create_result_filepath(output_dir,
                                   "extendedScanHistory",
                                   group_ID,
                                   "csv")

ScanHistory <- data.table::fread(filename)
```

- select valid entities

```{r, eval=FALSE}
result_files <- select_valid_image_files(ScanHistory,type = NULL)
```

- select hdr images and add filepath

```{r, eval=FALSE}
hdr_files <- select_hdr_files(result_files)
```

### single file

```{r, eval=FALSE}
image_path <- hdr_files$hdr_filepath[1]
blob_filename <- hdr_files$hdr_filename[1]
```

#### read_XML_BLOB_parameter() 

- reads single file
- in helpers: ImportBlobFiles

```{r, eval=FALSE}
blob_parameter <- read_XML_BLOB_parameter(image_path,
                                          blob_filename)

blob_parameter
```

#### functions that extract values from blob_parameter

- extract_h_pixels_from_blob_parameter() in helpers: ImportBlobFiles

```{r, eval=FALSE}
extract_h_pixels_from_blob_parameter(blob_parameter)
```

- extract_v_pixel_from_blob_parameter() in helpers: ImportBlobFiles

```{r, eval=FALSE}
extract_v_pixels_from_blob_parameter(blob_parameter)
```

- extract_n_pixels_from_blob_parameter() in helpers: ImportBlobFiles

```{r, eval=FALSE}
extract_n_pixels_from_blob_parameter(blob_paramter)
```

- extract_image_path_from_blob_parameter() in helpers: ImportBlobFiles

```{r, eval=FALSE}
extract_image_path_from_blob_parameter(blob_parameter)
```

- extract_encoding_from_blob_parameter() in helpers: ImportBlobFiles

```{r, eval=FALSE}
extract_encoding_from_blob_parameter(blob_parameter)
```

- convert_binsize_from_encoding() in helpers: ImportBlobFiles

```{r, eval=FALSE}
encoding <- extract_encoding_from_blob_parameter(blob_parameter)

convert_binsize_from_encoding(encoding)
```

- extract_image_width_from_blob_parameter() in helpers: ImportBlobFiles

```{r, eval=FALSE}
extract_image_width_from_blob_parameter(blob_paramter)
```

- extract_image_heigth_from_blob_parameter() in helpers: ImportBlobFiles

```{r, eval=FALSE}
extract_image_heigth_from_blob_parameter(blob_paramter)
```

- extract_image_resolution_from_blob_parameter() in helpers: ImportBlobFiles

```{r, eval=FALSE}
extract_image_resolution_from_blob_parameter(blob_parameter)
```

- extract_statistics_from_blob_parameter() in helpers: ImportBlobFiles

```{r, eval=FALSE}
extract_statistics_from_blob_parameter(blob_parameter)
```

- extract_parameter_from_BLOB in helpers: ImportBlobFiles

```{r, eval=FALSE}
extract_parameter_from_BLOB(image_path,
                            blob_filename)
```

- export_blob_parameter_of_image_filelist() in helpers: ImportBlobFiles

```{r, eval=FALSE}
hdr_files <- hdr_files%>%
  dplyr::rename("image_path"="hdr_filepath",
                "blob_filename" = "hdr_filename")

parameter_list<- export_blob_parameter_of_image_filelist(hdr_files,
                                                         output_dir,
                                                         paste0(group_ID,"_hdr_files"))
```

- read exported parameter list

```{r, eval=FALSE}
result_filename <- create_result_filepath(output_dir,
                                            "Blob_parameters",
                                            paste0(group_ID,"_hdr_files"),
                                            "csv")
parameter_list <- data.table::fread(result_filename)

parameter_list%>%head()
```

#### read_image_binary_file() 

- reads single file
- in helpers: ImportBlobFiles

```{r, eval=FALSE}
data <- read_image_binary_file(blob_parameter)
```

#### read_binary_image_as_matrix()

```{r, eval=FALSE}
read_binary_image_as_matrix <- function(image_path,
                                    blob_filename){
  
  blob_parameter <-read_XML_BLOB_parameter(image_path,
                                           blob_filename)
  
  data <- read_image_binary_file(blob_parameter)
  
  data_mat <- matrix(data,
                     nrow = attr(data, "v_pixel"),
                     ncol = attr(data,"h_pixel"))
  
  attr(data_mat, "image_resolution") <- attr(data,"image_resolution")
  
  return(data_mat)
}
```

## group of files

- nest file groups (by chip_ID and pos_ID) to a image_selection_list

```{r, eval=FALSE}
image_groups <- hdr_files%>%
  dplyr::group_by(chip_ID,pos_ID)%>%
  tidyr::nest()
```

- add group_ID 
- add filename of the file containing the data_sum results to be created

```{r, eval=FALSE}
image_groups <- image_groups%>%
  dplyr::mutate(group_ID = paste0(chip_ID,"_",pos_ID))%>%
  dplyr::mutate(data_file = create_result_filepath(output_dir,
                                                   "data_sum",
                                                   group_ID,
                                                   type="csv"))

image_group_list <- image_groups$data[[1]]
group_ID <-  image_groups$group_ID[1]
```

### create_export_data_sum()

- import all images of a image group
- calculate data_sum of all pixel values 
- return one image matrix
- exports data_sum into the output_dir

```{r, eval=FALSE}

create_export_data_sum <- function(image_group_list,
                                   group_ID,
                                   output_dir){
  
  create_working_directory(output_dir)
  
  for(i in 1:dim(image_group_list)[1]){
    
    image_path <- image_group_list$image_path[i]
    blob_filename <- image_group_list$blob_filename[i]
    
    data_mat <- read_binary_image_as_matrix(image_path,
                                            blob_filename)
    
    if(i == 1){
      data_sum <- data_mat
    }else{
      
      if(any(attr(data_mat,"image_resolution") != attr(data_sum,"image_resolution"))){
        writeLines(c(
          paste0("- image_resolution changed with scan_ID: ", image_group_list$scan_ID[i])
        ))}
      
      data_sum <- data_sum+data_mat
      
    }
  }
  
    result_filename <- create_result_filepath(output_dir,
                                            "data_sum",
                                            group_ID,
                                            type="csv")
    data_sum <- data.table::data.table(data_sum)
    data.table::fwrite(data_sum,
                       result_filename)
  
    return(attr(data_sum,"image_resolution"))

}
```

```{r, eval=FALSE}
data_sum_resultion <- create_export_data_sum(image_groups$data[[1]],
                                   image_groups$group_ID[1],
                                   output_dir)
```

- apply to complete chip_group

```{r, eval=FALSE}
image_groups <- image_groups%>%
  dplyr::mutate(data_sum_resultion = purrr::map2(data,
                                                 group_ID,
                                                 ~create_export_data_sum(.x,
                                                                         .y,
                                                                         file.path(output_dir,"data_sum_collection_2"))))

```

## workflow - find all imaga files

### list all files in image dirs

- export_list_all_image_files() in helpers: ImportBlobFiles

```{r, eval=FALSE}
image_files <- export_list_all_image_files(chip_IDs,
                                           group_ID,
                                           output_dir)
```

- create_result_filepath() in helpers: ImageProcessing

```{r, eval=FALSE}
file <- create_result_filepath(output_dir,
                               name_string = "all_image_files_of_groupID",
                               result_ID=group_ID,
                               type = "csv")
image_files <- data.table::fread(file)
```

- select_valid_image_files() in helpers: ImportBlobFiles

```{r, eval=FALSE}
blob32_files <- select_valid_image_files(image_files,
                                         type = "blob32")
```

### find_picture_informations()

```{r,eval=FALSE}
find_picture_informations<- function(image_path, blob_file_name, positions) {
  
  #  path<-paste0('\\\\ZKWSCANSRV2\\imagedata\\leipzig_volume0\\',image_path,'\\',positions[1,"positions"],'\\hdr\\',positions[1,"blob_file_name"],".blob32.xml")%>%
  path<-paste0(position_path,'\\',positions,'\\hdr\\',blob_file_name,".blob32.xml")%>%
    file.path()
  
  file<-read_xml(path)
  
  size<-file%>%xml_child("size")%>%xml_attrs("size")
  structure<-file%>%xml_child("data-structure")%>%xml_attrs("data-structure")
  statistics<-file%>%xml_child("metadata")%>%xml_child("statistics")%>%xml_attrs("statistics")  
  picture_size<-file%>%xml_child("metadata")%>%xml_child("extent")%>%xml_attrs("extent")
  
  parameter<-c(size,structure,statistics,picture_size)
  
  return(parameter)
}
```

### read_image_bin()

```{r,eval=FALSE}
read_image_bin <- function(image_path, position, blob_file_name, parameter) {
  
  #parameter<-pos['parameter']%>%flatten()
  parameter<-parameter%>%flatten()
  encoding<-parameter[["parameter"]][["encoding"]]
  
  bin_size<-case_when(encoding == "32bit-little-endian" ~ 4,
                      encoding == "16bit-little-endian" ~ 2)
  
  width<-parameter[["parameter"]][["width"]]%>%as.numeric()
  height<-parameter[["parameter"]][["height"]]%>%as.numeric()
  n_pixels<-width * height
  
  #path<-paste0('\\\\ZKWSCANSRV2\\imagedata\\leipzig_volume0\\',image_path,'\\',pos$positions,'\\hdr\\',pos$blob_file_name,".blob32")%>%
  path<-paste0(image_path,'\\',position,'\\hdr\\',blob_file_name,".blob32")%>%
    file.path()
  
  data<-readBin(path,
                integer(),
                n=n_pixels,
                size=bin_size)
  
  return (data)
}
```

### find_hdr_data ()

```{r,eval=FALSE}
find_hdr_data<-function(scan_IDs){
  
  
  # find all local server_path (where data could be)
  ##################################################
  
  server_path<-query_mongoDB(search_value="ImageServerPath",
                             mongo_collection = "limslager",
                             search_object = "EDLType",
                             return_columns = c("FlagEmpty","EDLName"))%>% #,"Do_Not_Check" gibts gar nicht
    filter(FlagEmpty == 0)
  
  # find basePath to the image folder
  ###################################
  
  file_path<-scan_IDs%>%
    mutate(file_path=map(ScanID,
                         ~ query_mongoDB(search_value=.x,
                                         mongo_collection = "scans",
                                         search_object = "UID",
                                         return_columns = "basePath")))%>%
    unnest(file_path)%>%
    select(basePath,everything())
  
  # find for ech ScanID the server_path, where the data could be found and add a new column server_path
  #####################################################################################################
  
  file_path$server_path<-NA
  file_path<-file_path%>%
    select(server_path,everything())
  
  for (k in 1:dim(file_path)[1]){
    
    file_path[k,'server_path']<-find_server_path(server_path = server_path$EDLName,
                                                 file_path = file_path[k,'basePath'])
    
  }
  
  
  # loop through all ScanID
  #########################
  
  data_collection<-list()
  
  for (j in 1:dim(file_path)[1]){
    
    
    # find all positions of a scan
    ###############################
    
    #image_path<-"M619946\\scanjobs\\EZKL150741"  #basePath
    
    position_path<-paste0(file_path[j,"server_path"],'\\',file_path[j,"basePath"])
    
    positions<-list.files(path=position_path)
    
    positions<-tibble(positions=positions[str_detect(positions,"pos")],)
    
    
    # finde für jede Position den Namen der binären hdr und der XML Datei
    #####################################################################
      
    positions<-positions%>%
      mutate(blob_file_name=map2_chr(position_path,positions,~get_blob_name(.x,.y)))
    
    
    # add picture characteristics of each hdr picture to positions df
    #################################################################
    
    positions<-positions%>%
      mutate(parameter = map2(blob_file_name,
                              positions,
                              ~ find_picture_informations(position_path, .x ,.y)))
    
    
    # read in the binary hdr image data and add column to positions
    ###############################################################
    
    data<-list()
    for(i in 1: dim(positions)[1]){
      
      data_read<-read_image_bin(position_path,positions[i,'positions'],positions[i,'blob_file_name'],positions[i,'parameter'])
      data_read<-list(meta_data=positions[i,],data=data_read)
      data<-c(data,list(data_read))
    }
    
    names(data)<-positions$positions
    data_collection<-c(data_collection,list(data))
    #rm(positions,position_path)
  }
  
  
  names(data_collection)<-scan_IDs$ScanID
  return(data_collection)
}
```

### check_hdr_import()

```{r,eval=FALSE}
check_hdr_import<-function(hdr_data){
  
  # extract statistic metadata from blob file
  data<-hdr_data$metadata
  
  statistics_metadata<-tibble::tibble(positions = hdr_data$positions)%>%
    mutate(mean_pixel=purrr::map_dbl(.x=data,~ .x["mean"]%>%as.numeric),
           median_pixel=purrr::map_dbl(.x=data,~ .x["median"]%>%as.numeric),
           min_pixel=purrr::map_dbl(.x=data,~ .x["min"]%>%as.numeric),
           max_pixel=purrr::map_dbl(.x=data,~ .x["max"]%>%as.numeric),
           n_distinct_pixel=purrr::map_dbl(.x=data,~ .x['distinct-values']%>%as.numeric))%>%
    tidyr::gather("parameter","value",-positions)%>%
    dplyr::mutate(origin ="metadata")

  # map through all positions and calculate statistics for imported hdr_data
  data<-hdr_data$data
  
  statistics_calculated<-tibble::tibble(positions = hdr_data$positions)%>%
    mutate(mean_pixel=purrr::map_dbl(.x=data,~ mean(.x)))%>%
    mutate(median_pixel=purrr::map_dbl(.x=data,~ median(.x)))%>%
    mutate(min_pixel=purrr::map_dbl(.x=data,~ min(.x)))%>%
    mutate(max_pixel=purrr::map_dbl(.x=data,~ max(.x)))%>%
    mutate(n_distinct_pixel=purrr::map_dbl(.x=data,~ length(unique(.x))))%>%
    tidyr::gather("parameter","value",-positions)%>%
    dplyr::mutate(origin ="calculated")%>%
    dplyr::mutate(value=round(value,digits=0))
  
  # join both statistic dataframes and compare values
  
  statistics <- rbind(statistics_calculated,statistics_metadata)%>%
    tidyr::spread(origin,value)
  
  quality <- dplyr::case_when(any(statistics$calculated != statistics$metadata) == FALSE ~ "OK",
                              # at least one parameter value differs (metadata compared to calculation)
                              any(statistics$calculated != statistics$metadata) == TRUE ~ "not OK", 
                              # if there where NA's
                              TRUE ~ "functional error") 
  return(quality)
}

```
