---
title: " documentation - import blob image data"
subtitle: "reportings on functional development"
author: "Julia Ortmann"
output: 
  html_document:
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: '3'
    theme:
      bg: "#202123"
      fg: "#B8BCC2"
      primary: "#EA80FC"
      secondary: "#00DAC6"
      base_font:
        google: Prompt
      heading_font:
        google: Proza Libre
abstract: The aim of this build functions for import of scan HDR images, defined by scan_ID
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_file = "inst/report/dev report - import scan HDR image data.html",
      envir = globalenv()
    )
  })
---

```{r setup, include=FALSE}
if (requireNamespace("thematic")) 
  thematic::thematic_rmd(font = "auto")
```

# summary

# workflow

- define chip_group and output_dir

```{r}
library(RJobTissueArea)
output_dir <- "devel/data/data_output"
group_ID <- "P1761451"
```

- create_working_directory() in helpers: RJob_execution

```{r}
RJobTissueArea:::create_working_directory(output_dir)
```

- load all chip_IDs in the group

```{r}
chip_IDs <- find_valid_group_chip_IDs(group_ID)
```

- create extended Version of ScanHistory

```{r, eval=FALSE}
ScanHistory <- create_ScanHistory_extended(chip_IDs,
                                           output_dir, 
                                           result_ID = group_ID)
```

- read ScanHistory

```{r}
filename <- create_result_filepath(output_dir,
                                   "extendedScanHistory",
                                   group_ID,
                                   "csv")

ScanHistory <- data.table::fread(filename)
```

- select valid entities

```{r}
result_files <- select_valid_image_files(ScanHistory,type = NULL)
```

- select hdr images and add filepath

```{r}
hdr_files <- select_hdr_files(result_files)
```

# define functions

## single file

```{r}
image_path <- blob32_files$image_path[1]
blob_filename <- blob32_files$blob_filename[1]
```

### read_XML_BLOB_parameter() 

- reads single file
- in helpers: ImportBlobFiles

```{r}
blob_parameter <- read_XML_BLOB_parameter(image_path,
                                          blob_filename)

blob_parameter
```

### functions that extract values from blob_parameter

- extract_h_pixels_from_blob_parameter() in helpers: ImportBlobFiles

```{r}
extract_h_pixels_from_blob_parameter(blob_parameter)
```

- extract_v_pixel_from_blob_parameter() in helpers: ImportBlobFiles

```{r}
extract_v_pixel_from_blob_parameter(blob_parameter)
```

- extract_n_pixels_from_blob_parameter() in helpers: ImportBlobFiles

```{r}
extract_n_pixels_from_blob_parameter(blob_paramter)
```

- extract_image_path_from_blob_parameter() in helpers: ImportBlobFiles

```{r}
extract_image_path_from_blob_parameter(blob_parameter)
```

- extract_encoding_from_blob_parameter() in helpers: ImportBlobFiles

```{r}
extract_encoding_from_blob_parameter(blob_parameter)
```

- convert_binsize_from_encoding() in helpers: ImportBlobFiles

```{r}
encoding <- extract_encoding_from_blob_parameter(blob_parameter)

convert_binsize_from_encoding(encoding)
```

- extract_image_width_from_blob_parameter() in helpers: ImportBlobFiles

```{r}
extract_image_width_from_blob_parameter(blob_paramter)
```

- extract_image_heigth_from_blob_parameter() in helpers: ImportBlobFiles

```{r}
extract_image_heigth_from_blob_parameter(blob_paramter)
```

- extract_image_resolution_from_blob_parameter() in helpers: ImportBlobFiles

```{r}
extract_image_resolution_from_blob_parameter(blob_parameter)
```

- extract_statistics_from_blob_parameter() in helpers: ImportBlobFiles

```{r}
extract_statistics_from_blob_parameter(blob_parameter)
```

- extract_parameter_from_BLOB in helpers: ImportBlobFiles

```{r}
extract_parameter_from_BLOB(image_path,
                            blob_filename)
```

- export_blob_parameter_of_image_filelist() in helpers: ImportBlobFiles

```{r, eval=FALSE}
parameter_list<- export_blob_parameter_of_image_filelist(blob32_files,
                                                         output_dir,
                                                         paste0(group_ID,"_blob32files"))
```

- read exported parameter list

```{r}
result_filename <- create_result_filepath(output_dir,
                                            "Blob_parameters",
                                            result_ID,
                                            "csv")
parameter_list <- data.table::fread(result_filename)

parameter_list%>%head()
```

### read_image_binary_file() 

- reads single file
- in helpers: ImportBlobFiles

```{r}
data <- read_image_binary_file(blob_parameter)
```

### read_binary_image_as_matrix()

```{r}
read_binary_image_as_matrix <- function(image_path,
                                    blob_filename){
  
  blob_parameter <-read_XML_BLOB_parameter(image_path,
                                           blob_filename)
  
  data <- read_image_binary_file(blob_parameter)
  
  data_mat <- matrix(data,
                     nrow = attr(data, "v_pixel"),
                     ncol = attr(data,"h_pixel"))
  
  attr(data_mat, "image_resolution") <- attr(data,"image_resolution")
  
  return(data_mat)
}
```

## group of files

- nest file groups (by chip_ID and pos_ID) to a image_selection_list

```{r}
image_groups <- blob32_files%>%
  dplyr::group_by(chip_ID,pos_ID)%>%
  tidyr::nest()
```

- add group_ID 
- add filename of the file containing the data_sum results to be created

```{r}
image_groups <- image_groups%>%
  dplyr::mutate(group_ID = paste0(chip_ID,"_",pos_ID))%>%
  dplyr::mutate(data_file = create_result_filepath(output_dir,
                                                   "data_sum",
                                                   group_ID,
                                                   type="csv"))

image_group_list <- image_groups$data[[1]]
group_ID <-  image_groups$group_ID[1]
```

### create_export_data_sum()

- import all images of a image group
- calculate data_sum of all pixel values 
- return one image matrix
- exports data_sum into the output_dir

```{r}

create_export_data_sum <- function(image_group_list,
                                   group_ID,
                                   output_dir){
  
  create_working_directory(output_dir)
  
  for(i in 1:dim(image_group_list)[1]){
    
    image_path <- image_group_list$image_path[i]
    blob_filename <- image_group_list$blob_filename[i]
    
    data_mat <- read_binary_image_as_matrix(image_path,
                                            blob_filename)
    
    if(i == 1){
      data_sum <- data_mat
    }else{
      
      if(any(attr(data_mat,"image_resolution") != attr(data_sum,"image_resolution"))){
        writeLines(c(
          paste0("- image_resolution changed with scan_ID: ", image_group_list$scan_ID[i])
        ))}
      
      data_sum <- data_sum+data_mat
      
    }
  }
  
    result_filename <- create_result_filepath(output_dir,
                                            "data_sum",
                                            group_ID,
                                            type="csv")
    data_sum <- data.table::data.table(data_sum)
    data.table::fwrite(data_sum,
                       result_filename)
  
    return(attr(data_sum,"image_resolution"))

}
```

```{r}
data_sum_resultion <- create_export_data_sum(image_groups$data[[1]],
                                   image_groups$group_ID[1],
                                   output_dir)
```

- apply to complete chip_group

```{r}
image_groups <- image_groups%>%
  dplyr::mutate(data_sum_resultion = purrr::map2(data,
                                                 group_ID,
                                                 ~create_export_data_sum(.x,
                                                                         .y,
                                                                         file.path(output_dir,"data_sum_collection"))))

```



 






































# supplement

## list all files in image dirs

- read list of all image files in a chip group

```{r}
file <- create_result_filepath(output_dir,
                               name_string = "all_image_files_of_groupID",
                               result_ID=group_ID,
                               type = "csv")
image_files <- data.table::fread(file)
```

- select_valid_image_files() in helpers: ImportBlobFiles

```{r}
blob32_files <- select_valid_image_files(image_files,
                                         type = "blob32")
```

## find_picture_informations()

```{r,eval=FALSE}
find_picture_informations<- function(image_path, blob_file_name, positions) {
  
  #  path<-paste0('\\\\ZKWSCANSRV2\\imagedata\\leipzig_volume0\\',image_path,'\\',positions[1,"positions"],'\\hdr\\',positions[1,"blob_file_name"],".blob32.xml")%>%
  path<-paste0(position_path,'\\',positions,'\\hdr\\',blob_file_name,".blob32.xml")%>%
    file.path()
  
  file<-read_xml(path)
  
  size<-file%>%xml_child("size")%>%xml_attrs("size")
  structure<-file%>%xml_child("data-structure")%>%xml_attrs("data-structure")
  statistics<-file%>%xml_child("metadata")%>%xml_child("statistics")%>%xml_attrs("statistics")  
  picture_size<-file%>%xml_child("metadata")%>%xml_child("extent")%>%xml_attrs("extent")
  
  parameter<-c(size,structure,statistics,picture_size)
  
  return(parameter)
}
```

## read_image_bin()

```{r,eval=FALSE}
read_image_bin <- function(image_path, position, blob_file_name, parameter) {
  
  #parameter<-pos['parameter']%>%flatten()
  parameter<-parameter%>%flatten()
  encoding<-parameter[["parameter"]][["encoding"]]
  
  bin_size<-case_when(encoding == "32bit-little-endian" ~ 4,
                      encoding == "16bit-little-endian" ~ 2)
  
  width<-parameter[["parameter"]][["width"]]%>%as.numeric()
  height<-parameter[["parameter"]][["height"]]%>%as.numeric()
  n_pixels<-width * height
  
  #path<-paste0('\\\\ZKWSCANSRV2\\imagedata\\leipzig_volume0\\',image_path,'\\',pos$positions,'\\hdr\\',pos$blob_file_name,".blob32")%>%
  path<-paste0(image_path,'\\',position,'\\hdr\\',blob_file_name,".blob32")%>%
    file.path()
  
  data<-readBin(path,
                integer(),
                n=n_pixels,
                size=bin_size)
  
  return (data)
}
```

## find_hdr_data ()

```{r,eval=FALSE}
find_hdr_data<-function(scan_IDs){
  
  
  # find all local server_path (where data could be)
  ##################################################
  
  server_path<-query_mongoDB(search_value="ImageServerPath",
                             mongo_collection = "limslager",
                             search_object = "EDLType",
                             return_columns = c("FlagEmpty","EDLName"))%>% #,"Do_Not_Check" gibts gar nicht
    filter(FlagEmpty == 0)
  
  # find basePath to the image folder
  ###################################
  
  file_path<-scan_IDs%>%
    mutate(file_path=map(ScanID,
                         ~ query_mongoDB(search_value=.x,
                                         mongo_collection = "scans",
                                         search_object = "UID",
                                         return_columns = "basePath")))%>%
    unnest(file_path)%>%
    select(basePath,everything())
  
  # find for ech ScanID the server_path, where the data could be found and add a new column server_path
  #####################################################################################################
  
  file_path$server_path<-NA
  file_path<-file_path%>%
    select(server_path,everything())
  
  for (k in 1:dim(file_path)[1]){
    
    file_path[k,'server_path']<-find_server_path(server_path = server_path$EDLName,
                                                 file_path = file_path[k,'basePath'])
    
  }
  
  
  # loop through all ScanID
  #########################
  
  data_collection<-list()
  
  for (j in 1:dim(file_path)[1]){
    
    
    # find all positions of a scan
    ###############################
    
    #image_path<-"M619946\\scanjobs\\EZKL150741"  #basePath
    
    position_path<-paste0(file_path[j,"server_path"],'\\',file_path[j,"basePath"])
    
    positions<-list.files(path=position_path)
    
    positions<-tibble(positions=positions[str_detect(positions,"pos")],)
    
    
    # finde für jede Position den Namen der binären hdr und der XML Datei
    #####################################################################
      
    positions<-positions%>%
      mutate(blob_file_name=map2_chr(position_path,positions,~get_blob_name(.x,.y)))
    
    
    # add picture characteristics of each hdr picture to positions df
    #################################################################
    
    positions<-positions%>%
      mutate(parameter = map2(blob_file_name,
                              positions,
                              ~ find_picture_informations(position_path, .x ,.y)))
    
    
    # read in the binary hdr image data and add column to positions
    ###############################################################
    
    data<-list()
    for(i in 1: dim(positions)[1]){
      
      data_read<-read_image_bin(position_path,positions[i,'positions'],positions[i,'blob_file_name'],positions[i,'parameter'])
      data_read<-list(meta_data=positions[i,],data=data_read)
      data<-c(data,list(data_read))
    }
    
    names(data)<-positions$positions
    data_collection<-c(data_collection,list(data))
    #rm(positions,position_path)
  }
  
  
  names(data_collection)<-scan_IDs$ScanID
  return(data_collection)
}
```

## check_hdr_import()

```{r,eval=FALSE}
check_hdr_import<-function(hdr_data){
  
  # extract statistic metadata from blob file
  data<-hdr_data$metadata
  
  statistics_metadata<-tibble::tibble(positions = hdr_data$positions)%>%
    mutate(mean_pixel=purrr::map_dbl(.x=data,~ .x["mean"]%>%as.numeric),
           median_pixel=purrr::map_dbl(.x=data,~ .x["median"]%>%as.numeric),
           min_pixel=purrr::map_dbl(.x=data,~ .x["min"]%>%as.numeric),
           max_pixel=purrr::map_dbl(.x=data,~ .x["max"]%>%as.numeric),
           n_distinct_pixel=purrr::map_dbl(.x=data,~ .x['distinct-values']%>%as.numeric))%>%
    tidyr::gather("parameter","value",-positions)%>%
    dplyr::mutate(origin ="metadata")

  # map through all positions and calculate statistics for imported hdr_data
  data<-hdr_data$data
  
  statistics_calculated<-tibble::tibble(positions = hdr_data$positions)%>%
    mutate(mean_pixel=purrr::map_dbl(.x=data,~ mean(.x)))%>%
    mutate(median_pixel=purrr::map_dbl(.x=data,~ median(.x)))%>%
    mutate(min_pixel=purrr::map_dbl(.x=data,~ min(.x)))%>%
    mutate(max_pixel=purrr::map_dbl(.x=data,~ max(.x)))%>%
    mutate(n_distinct_pixel=purrr::map_dbl(.x=data,~ length(unique(.x))))%>%
    tidyr::gather("parameter","value",-positions)%>%
    dplyr::mutate(origin ="calculated")%>%
    dplyr::mutate(value=round(value,digits=0))
  
  # join both statistic dataframes and compare values
  
  statistics <- rbind(statistics_calculated,statistics_metadata)%>%
    tidyr::spread(origin,value)
  
  quality <- dplyr::case_when(any(statistics$calculated != statistics$metadata) == FALSE ~ "OK",
                              # at least one parameter value differs (metadata compared to calculation)
                              any(statistics$calculated != statistics$metadata) == TRUE ~ "not OK", 
                              # if there where NA's
                              TRUE ~ "functional error") 
  return(quality)
}

```
