---
title: "HowToInstall"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HowToInstall}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
usethis::proj_set()
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache=FALSE
)

knitr::opts_knit$set(cache=FALSE,
                     root.dir=file.path(getwd()),
                     base.dir=file.path(getwd())
)

here::here()
here::i_am("vignettes/HowToInstall.Rmd")

```

1.  setup your system:

    > -   install R 3.6.3
    >
    >     <https://cran.r-project.org/bin/windows/base/old/3.6.3/>
    >
    > -   install RStudio
    >
    >     <https://www.rstudio.com/products/rstudio/download/#download>
    >
    > -   install the R packages needed for installation by executing the following code in RStudio:
    >
    >         install.packages(c("devtools","installr","remotes"))
    >
    > -   install RTools 35 by executing the following code in RStudio:
    >
    >         installr::install_rtools()
    >
    > -   install the R package mongolite 1.0 by executing the following code in RStudio:
    >
    >          remotes::install_version("mongolite","1.0")
    >
    > -   install Bioconductor packages
    >
    >          remotes::install_version("locfit",version="1.5.9.4")
    >
    >          BiocManager::install("EBImage",force=TRUE)

2.  get and install the actual version of the *ZKW TissueArea calculation R package*:

    > -   go to Github webpage:
    >
    >     <https://github.com/juleZWK/RJobTissueArea/>
    >
    > -   klick on newest release and download it
    >
    > -   choose the tar.gz file and save it on your local disk
    >
    > -   in RStudio set the path and the name of the tar.gz file
    >
    >         package_dir <- choose.dir()
    >         package_name <- "RJobTissueArea_0.0.0.13.tar.gz"
    >
    > -   install the ZKW distance calculation package by executing the following code in RStudio:
    >
    >         devtools::install(file.path(package_dir, package_name), dependencies = TRUE)

3.  start your analysis in RStudio:

    > -   in RStudio create a "New Project" and name it approbiately or select a existing project, where you want to add the distance calculation
    >
    > -   create a "New File" and choose the "RMarkdown" file type
    >
    > -   select "From Template" and choose the "ExampleReport" template
    >
    > -   save a copy into your project directory and follow instructions in the template

💌 *please feedback any issues occurring during installation*

### supporting notes

-   The **developmental package** version can be installed from github repository directly. To do so, execute the following code in RStudio.:

        devtools::install_github("juleZWK/RJobTissueArea")

-   If you need to have the flowCore package installed:

    ```{r,eval=FALSE}
    if (!requireNamespace("BiocManager", quietly = TRUE))
        install.packages("BiocManager")

    BiocManager::install("flowCore")
    ```
