---
title: "HowToInstall"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HowToInstall}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
usethis::proj_set()
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache=FALSE
)

package_dir <- rprojroot::find_rstudio_root_file()
knitr::opts_knit$set(cache=FALSE,
                     root.dir=package_dir,
                     base.dir=file.path(package_dir,"vignettes","figures"))

here::here()
here::i_am("vignettes/HowToInstall.Rmd")

```

1.  setup PC for using R:

    > -   install R 3.6.3
    >
    >     <https://cran.r-project.org/bin/windows/base/old/3.6.3/>
    >
    > -   install RStudio
    >
    >     <https://www.rstudio.com/products/rstudio/download/#download>
    >
    > -   install the R packages needed for installation by executing the following code in RStudio:
    >
    >         install.packages("installr")
    >
    > -   install RTools 35 by executing the following code in RStudio:
    >
    >         installr::install_rtools()

2.  setup R for using this package:

    > -   install internal R tools:
    >
    >         install.packages(c("remotes","biocmanager"))
    >
    > -   install a package needed for accessing the mongoDB
    >
    >         remotes::install_version("mongolite","1.0")
    >
    > -   install packages needed for image processing
    >
    >         remotes::install_version("locfit",version="1.5.9.4") 
    >         BiocManager::install("EBImage",force=TRUE)

3.  get and install the actual version of the *RJobTissueArea package*:

    > -   go to Github webpage:
    >
    >     <https://github.com/Canopy-Biosciences/RJobTissueArea/>
    >
    > -   klick on newest release and download it
    >
    > -   choose the tar.gz file and save it on your local disk
    >
    > -   in RStudio set the path and the name and version of the tar.gz file on your local disk by editing the following code
    >
    >         package_dir <- choose.dir()
    >         package_name <- "RJobTissueArea"
    >         package_version <- "x.x.x.x."tar.gz"
    >
    > -   install the ZKW distance calculation package:
    >
    >         pkg <- paste0(package_name,"_",package_version,"tar.gz")
    >         pkg_path <- file.path(package_dir, pkg)
    >         devtools::install(pkg_path, dependencies = TRUE)

4.  start your analysis in RStudio:

    > -   in RStudio create a "New Project" and name it approbiately or select a existing project, where you want to add the distance calculation
    >
    > -   create a "New File" and choose the "RMarkdown" file type
    >
    > -   select "From Template" and choose a template (e.g. "estimateTissueArea")
    >
    > -   save a copy into your project directory and follow instructions in the template

💌 *please feedback any issues occurring during installation*

### supporting notes

-   The **developmental package** version can be installed from github repository directly. To do so, execute the following code in RStudio.:

        devtools::install_github("Canopy-Biosciences/RJobTissueArea")

-   If you need to have the flowCore package installed:

    ```{r,eval=FALSE}
    if (!requireNamespace("BiocManager", quietly = TRUE))
        install.packages("BiocManager")

    BiocManager::install("flowCore")
    ```
